Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-10-06 paper/paper.tex
_bioRxiv_ and initial _eLife_ submission version

But although viral variation is clearly important, it still only partially explains heterogeneity among influenza-infected cells.
We find substantial breadth in viral transcriptional burden and occasional IFN induction even among cells infected with fully wild-type virions.
Additionally, none of the viral defects in IFN+ cells induce IFN deterministically in our validation experiments---and the apparently most immunostimulatory defect (absence of NS) also occurs in multiple IFN- cells in our single-cell dataset.
Of course, our single-cell virus sequencing only calls mutations present in a cell at relatively high frequency, and so could overlook low-frequency mutations that might contribute to IFN induction.
However, we suspect that stochasticity or pre-existing cellular states also affect the outcome of infection, since heterogeneity in IFN induction is present even among cells treated with synthetic innate-immune ligands~\citep{shalek2013single, shalek2014single, wimmers2018single, bhushal2017cell}, as well as for other viruses~\citep{oneal2018west}.

>>>>

But although viral variation is clearly important, it still only partially explains heterogeneity among influenza-infected cells.
We find substantial breadth in viral transcriptional burden and occasional IFN induction even among cells infected with fully wild-type virions.
Additionally, none of the viral defects in IFN+ cells induce IFN deterministically in our validation experiments---and the apparently most immunostimulatory defect (absence of NS) also occurs in multiple IFN- cells in our single-cell dataset.
Of course, our single-cell virus sequencing only calls mutations present in a cell at relatively high frequency, and so could overlook low-frequency mutations that contribute to IFN induction.
However, we suspect that stochasticity or pre-existing cellular states also affect the outcome of infection, since heterogeneity in IFN induction is present even among cells treated with synthetic innate-immune ligands~\citep{shalek2013single, shalek2014single, wimmers2018single, bhushal2017cell}, as well as for other viruses~\citep{oneal2018west}.
